Individual Variation in Animal Movement and Effects on Seed Dispersal Distance

### 2021-02-05 paper/paper.Rmd
methods done with thresholds from diagnostic pltos

Our study focused on long-distance dispersal events defined as any dispersal event over 500m from the parent tree in order to compare our results to previous studies in this same ecological system [@holbrook_dispersal_2009; @holbrook_home_2011; @holbrook_using_2007]. However, when selecting a threshold for a POT approach, it is also possible to use diagnostic plots by fitting the data to a sequence of thresholds, with the goal of finding the lowest threshold that provides similar parameter values to any other higher threshold. We performed these analysis (Supplementary information), and given that parameter estimates were similar, we report our parameter estimates and expected probability of occurrence of long-distance events using our original 500m threshold. We fit Generalized Pareto distributions to the data via maximum likelihood using the package extRemes [@extRemes2] in R [@Rcit].

>>>>

Our study focused on long-distance dispersal events defined as any dispersal event over 500m from the parent tree in order to compare our results to previous studies in this same ecological system [@holbrook_dispersal_2009; @holbrook_home_2011; @holbrook_using_2007]. However, when selecting a threshold for a POT approach, it is also possible to use diagnostic plots by fitting the data to a sequence of thresholds, with the goal of finding the lowest threshold that provides similar parameter values to any other higher threshold. We performed these analysis and we report our parameter estimates and expected probability of occurrence of long-distance events using the thresholds from diagnostics plots. We fit Generalized Pareto distributions to the data via maximum likelihood using the package extRemes [@extRemes2] in R [@Rcit].
